---
title: "dawn-cheung"
output: html_document
---

*Welcome to the data story of the world's digital inequality, and why it kinda sucks!*

This very webpage is a testament to how far digital technologies have come. All of the data presented collated here, and the tools used for collation (Rstudio, Quarto, various library packages, etc) were accessed and/or downloaded from the internet with a clunky old laptop. Hence, you would think that once this data story is published online, virtually anyone could access it! However, this is clearly not the case. <br><br>

Below is a widget that shows, across space, 3 key factors that affects one's ability to use the internet:

-   physical access to the internet (i.e. the availability of the relevant infocomm technologies, like cell towers and electronic devices),

-   the price of internet, and

-   speed of internet (the widget uses download speed which is basically how fast you can receive information from the web). <br>

You might be wondering: "Why go beyond access to the internet? As long as the resource is physically available, isn't that enough?" Well, imagine I opened an uncooked meat store in every country and city in the world. Everyone can buy infinite meat; global hunger solved! But some people don't have access to stoves or spaces to make fires to cook the meat, some people are allergic to/can't eat meat, maybe at some locations I only sell meat scraps that are about to go bad, and perhaps the most obvious caveat: some people simply can't afford the meat, even if its right there in my store. The same goes for the internet.

The access, price and speed of internet are equally important for digital equity. The graphs after this widget will further demonstrate the impact of all 3 factors, but if the widget below still hasn't loaded yet, I think that's a pretty solid case for why internet speed so important.

<iframe height="435" width="110%" frameborder="no" src="https://myshinyappplease.shinyapps.io/MyShinyApp/">

</iframe>

On a more serious note, if the widget still refuses to load, try switching off background processes (eg Youtube, Spotify, Canvas, Discord, etc), then reload the page. Otherwise, try this link instead <a href = https://myshinyappplease.shinyapps.io/MyShinyApp/>https://myshinyappplease.shinyapps.io/MyShinyApp/</a>. As a last resort, restart your computer, use someone elses computer with a higher RAM capacity, or download the application files from <a href = https://github.com/dawn-cheung/dawn-cheung.github.io/tree/main/MyShinyApp>my github</a> and run "app.R" on your local machine.<br><br><br>

```{r unbroken, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6, fig.width = 14}
library(tidyverse)
library(ggplot2)
library(maps)
library(sf)
library(dplyr)
library(countrycode)
library(shiny)
library(ggpubr)
library(rsconnect)
library(plotly)
library(forcats)

#HARDCODE ALL DATASETS INTO ISO3: DONE

# Import the data with coordinates
world_map <- map_data("world")
world_map$region <- countrycode(world_map$region, "country.name", "iso3c")

access_dataset <- read.csv("accesstointernet.csv")
speed_dataset <- read.csv("worldwideInternetSpeed.csv")
price_dataset <- read.csv("worldwideMobileDataPricing2019to2023.csv")

#filter by year
accessyear <- access_dataset %>% filter(Dyear == "D2020")
speedyear <- speed_dataset %>% filter(Dyear == "D2020")
priceyear <- price_dataset %>% filter(Dyear == "D2020")

econineq <- read.csv("EconomicInequality.csv") #ISO3 used
desidata <- read.csv("desi-data.csv") #ISO3 used!
gdpPERCAPITA <- read.csv("gdpPERCAPITA.csv")

econindicator <- econineq %>% 
  filter(year == 2020) #%>% #MY PROPOSED SOLUTION: use gini ONLY FOR COLOURATION. do NOT use gini values for xy values
  #filter(scale == "Equivalized")
gdpPERCAPITA <- gdpPERCAPITA %>% filter(year == 2020)

econindicator$gini <- as.numeric(econindicator$gini)
gdpPERCAPITA$GDP.per.capita <- as.numeric(gdpPERCAPITA$GDP.per.capita)
speedyear$values <- as.numeric(speedyear$values)
priceyear$values <- as.numeric(priceyear$values)

accessscatter <- left_join(econindicator, accessyear, by = "region")  %>%
  left_join(. , gdpPERCAPITA, by = "region")
accessscatter %>%  #KEEPING
        drop_na(values) %>%
  ggplot(data = accessscatter, mapping = aes(x = values, y = log(GDP.per.capita), colour = gini)) +
  geom_point() + 
  labs(x = "Percentage of the population accessing the Internet (%)", y = "logarithm of GDP per capita", title = "How access to the internet affects economic output") +
  geom_smooth(method="lm", col="black")  +
  theme(plot.title=element_text(size=30))
```

insert flavour text explaining whats gg on <br><br><br>

```{r PRICEoverACCESS, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 11, fig.width = 14}
accessyear <- accessyear %>% rename(percent_access = values)
priceyear <- priceyear %>% rename(price = values)
speedyear <- speedyear %>% rename(speedyear_values = values)

priceaccessscatter <- left_join(accessyear, priceyear, by = "region") %>%
  left_join(. , econindicator, by = "region")

ggplotly(priceaccessscatter %>% 
        drop_na(priceyear, accessyear) %>%
  ggplot(data = priceaccessscatter, mapping = aes(x = price, y = percent_access, colour = Continental.region)) +
  geom_point() + 
  labs(x = "Price of Internet (USD$)", y = "Percentage of the population accessing the Internet (%)", title = "How price of internet affects access to the internet", colour = "Continental Region") +
  geom_smooth(method="lm", col="black")  +
  theme(plot.title=element_text(size=26)),
  plot.margin = margin(0.05, 1.3, 0.05, 0.05, "cm"))

accessyear <- accessyear %>% rename(values = percent_access)
priceyear <- priceyear %>% rename(values = price)
speedyear <- speedyear %>% rename(values = speedyear_values)
```

insert flavour text explaining whats gg on<br><br>

```{r GDPoverSPEED, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6, fig.width = 14}
speedscatter <- left_join(econindicator, speedyear, by = "region")  %>%
  left_join(. , gdpPERCAPITA, by = c("region", "year"))
speedscatter %>% #KEEPING
  drop_na(values) %>%
  ggplot(data = speedscatter, mapping = aes(x = values, y = GDP.per.capita, colour = gini)) +
  geom_point() + 
  labs(x = "Speed of Internet (Mpbs)", y = "GDP per capita (USD$)", title = "How economic development affects mean speed of internet") +
  geom_smooth(method="lm", col="black")  +
  theme(plot.title=element_text(size=30)) +
  geom_vline(xintercept=2.5, linetype="dashed", color = "red") +
  geom_vline(xintercept=15, linetype="dashed", color = "red") +
  annotate(geom="text", x=3, y=98000, label=str_wrap("Official bandwith requirements needed for Zoom to function", 15), color="black", fontsize=6, hjust = "left", lineheight = 0.8) +
  annotate(geom="text", x=15.6, y=82900, label=str_wrap("Zoom functions, but experiences buffer & poor video and audio quality", 20), color="black", fontsize=6, hjust = "left", lineheight = 0.8)
```

insert flavour text explaining whats gg on <br><br><br>

```{r desi-tester, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6, fig.width = 14}
accessyear <- access_dataset %>% filter(Dyear == "D2022")
desi <- desidata %>%
  filter(period == 2022) %>%
  group_by(region) %>%
  mutate(desi_values = sum(values)) %>%
  ungroup()

desiscatter <- left_join(desi, accessyear, by = "region")  %>%
  left_join(. , gdpPERCAPITA, by = "region") %>%
  drop_na(region)

ggplot(desiscatter, aes(fct_reorder(Country.Name, GDP.per.capita), desi_values, fill = indicator)) +
  geom_col() +
  labs(x = "Countries ranked by GDP per capita", y = "Digital skill by DESI index", title = "How economic development affects digital skills") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_fill_discrete(name="DESI indicator (% of population)",
                     labels=c("1a2: Basic digital skills","1a3: Above basic digital skills","1a6: Females having at least basic skills"))+
  theme(plot.title=element_text(size=30),
        axis.text.x = element_text(vjust = 0.5 , size = 7.8))
accessyear <- access_dataset %>% filter(Dyear == "D2020")
```

Did you know that the World Wide Web originated from Europe? Despite the EU being the birthplace of the internet, there is still significant digital inequality within the EU. This graph shows that within the EU, ***lower economic development impedes the population's digital skills**. As GDP increases, the proportion of the country's population with basic digital skills, above basic digital skills, and females possessing digital skills increases.* This means that in countries like Bulgaria and Romania, even if you have an internet connection, you might not have the skills to use the digital tools and resources discerningly and/or appropriately, which means you're more likely to fall for online scams and fake news.<br><br><hr>

So now the question is, how does the internet benefit *people,* or in other words,

<h1>How does the internet act as an enabler?</h1>

There are many good things that good internet can bring about. The 4 factors I'd like to bring up are: increased access to knowledge and information, enhancing education and educational institutions, strengthening democracy and increasing socio-emotional wellbeing.

<h2>*KNOWLEDGE AND INFORMATION*</h2>

```{r 3i-survey-pie-charts, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6.5, fig.width = 14}
AgreeDisagreePie <- function(percent, my_title, title_size) {
  percent = as.numeric(percent)
  data <- data.frame("category" = c('Agree', 'Disagree'), "amount" = c(percent, 100-percent))
  ggplot(data, aes(x="", y=amount, fill=category)) +
    geom_bar(stat="identity", width=1) +
    coord_polar("y") +
    labs(title = str_wrap(my_title, 40)) +
    geom_text(aes(label = paste0(amount, "%")), position = position_stack(vjust = 0.5), size = 8.2) +
    theme_void() +
    theme(plot.title = element_text(size = title_size),
          plot.margin = margin(0, 1, 0, 1, "cm"))
}

ggarrange(AgreeDisagreePie(73, "Being able to use the internet to access information and express opinions should be a human right", 16),
          AgreeDisagreePie(60.1, "I use the internet to find information (#1 Most popular use case globally)", 16),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend = "bottom",
          align = "hv")
```

<h2>*EDUCATION*</h2>

```{r EDUCATION-survey-pie-charts, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6.5, fig.width = 14}
ggarrange(AgreeDisagreePie(67, "Using the internet has helped me pursue my education or that of my household members", 16),
          AgreeDisagreePie(39, "I use the internet for education and study-related purposes (#10 Most popular use case globally)", 16),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend = "bottom",
          align = "hv")
```

<h2>*DEMOCRACY*</h2>

```{r DEMOCRACY-survey-pie-charts, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6.5, fig.width = 14}
ggarrange(AgreeDisagreePie(51.8, "I use the internet to keep up-to-date with news and events (#3 Most popular use case globally)", 16),
          AgreeDisagreePie(64, "I feel that social media is effective in getting elected officials to pay attention to issues)", 16),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend = "bottom",
          align = "hv")
```

<h2>*SOCIO-EMOTIONAL WELLBEING*</h2>

```{r WELLBEING-survey-pie-charts, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6.5, fig.width = 14}
ggarrange(AgreeDisagreePie(51.8, "I use the internet to stay in touch with friends and family (#2 Most popular use case globally)", 16),
          AgreeDisagreePie(51.1, "I use the internet to watch videos, TV shows, or movies (#4 Most popular use case globally)", 16),
          ncol = 2, nrow = 1,
          common.legend = TRUE, legend = "bottom",
          align = "hv")
```

<h1>*TO CONCLUDE*</h1>

```{r final-survey-pie-charts, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height = 6.2, fig.width = 14}
AgreeDisagreePie(66, "The internet has improved life in my country", 30)
```

insert flavour text explaining whats gg on <br><br><br>

\(1\) Hi! I'm Dawn, a year one communications and new media student. I like to bake but no one eats what I make.\
\
(2) github folder: <https://github.com/dawn-cheung/NM2207-Folder-Upload>
